PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Corrected COPING GLAD OCI-R participant IDs

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

>>>>

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

  drop_na(recipientFirstName) %>% # Drop NAs
  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
